VIP-193: Committee-Based POA

### 2020-02-27 article.tex
ongoing final verison

\section{Overview}
The Proof-of-Authority consensus algorithm~\cite{VWP18}, or POA in short, is efficient of using network bandwidth. It divides time into rounds with a fixed length and assumes that the majority of its (authorized) nodes perform consensus in the same round. In each round, nodes select a leader (the node responsible for generating a new block) based on the round number, block height and their local views of active nodes. Therefore, the procedure can be considered instant, which allows more time for transmitting transaction (TX) data in each consensus round.

POA relies on the staked reputation (by nodes) and economic incentives to keep the system secure. However, it cannot stop malicious leaders causing temporary inconsistency. To improve the security of POA, we propose to introduce a committee to endorse the new block generated in each consensus round. The verifiable random function~(VRF)~\cite{PapEtAl99} is used for nodes to locally decide their committee memberships. With the committee mechanism, a malicious leader would have to collude with the committee to cause inconsistency. However, the property of VRF guarantees that the committee is selected randomly. Therefore, it makes it much more difficult for adversaries to launch such attacks.

We assume that the network is synchronous and the messages are transmitted through gossip communication, i.e., if an honest node sends a message or an honest node receives a message, all other honest nodes will receive same message within at most a delay of $\tau$, which is determined by the network configuration and known in advance.

%Note that besides the network synchrony, we also assume that messages be transmitted through gossip communication. Hence, if an honest node receives a message, all other honest nodes will receive the same message with a bounded delay. 
\section{Specifications}
\subsection{Notations}
\renewcommand{\arraystretch}{2}
\begin{longtable}{p{3cm} p{10cm}}
    Symbol  & Description \\
    \hline\hline
    $N$ & Total number of nodes \\
    \hline
    $u=1,2,\dots,N$ & node index \\
    \hline
    $H(\cdot)$ & Cryptographic hash function \\
    \hline
    ${\tt SIG}_u(\cdot)$ & Signature of $u$ \\
    \hline
    ${\tt PK}_u$ & Public key of $u$ \\
    \hline
    ${\tt SK}_u$ & Private key of $u$ \\
    \hline
    $\rho\left(\cdot\right)$ & Merkle root of the input set\\
    \hline
    $r$ & Consensus round number \\
    \hline
    $l_r=1,2,...,N$ & Leader in round $r$ \\
    \hline
    $s_r$ & Block summary produced by $l_r$ \\
    \hline
    $\tau_r$ & $s_r\,\|\,{\tt Sig}_{\,l_r}(s_r)$ \\
    \hline
    $\epsilon$ & Predefined threshold to determine committee memberships \\
    \hline
    $d$ & Number of endorsements required for forming a valid block \\
    \hline
    $\Sigma_r$ & Pending transaction set prepared by $l_r$ \\
    \hline
    $B_{u,r}^*$ & Last block of the canonical chain recognized by $u$ in round $r$\\ 
    \hline
    $H_{vrf},\Pi_{vrf},V_{vrf}$ & Functions that compute hash, generate proof and verify proof defined in the VRF scheme, respectively \\
    \hline
    ${\tt M}_{\,r}$ & Common VRF message generated for committee selection \\
    \hline
    $\omega$, $\omega^*$ & Branch and trunk \\
    \hline
    $m$, $L$ & Epoch number and the number of consensus rounds in one epoch \\
    \hline
    $b_m$ & Random beacon computed using randomness from the last block of the $m$'th epoch \\
    \hline
\end{longtable}

\subsection{Committee Membership}
\label{sec:committee}
The verifiable random function can be considered as a public-key version of keyed cryptographic hash. The hash of a given message can only be computed by the owner of the private key and can be verified by anyone given the public key~{\tt SK} and message~{\tt M}. The scheme defines the following functions:
\begin{itemize}
    \item $\pi\leftarrow\Pi_{vrf}({\tt SK},{\tt M})$ - function that generates VRF proof;
    \item $\{{\tt TRUE}, {\tt FALSE}\}\leftarrow V_{vrf}({\tt SK},{\tt M},\pi)$ - function that verify VRF proof;
    \item $h\leftarrow H_{vrf}({\tt SK},{\tt M})=H(\pi)$ - function that computes the hash.
\end{itemize}

Node~$u$ determines his committee membership by Algorithm~\ref{alg:committee-gen}. Here ${\tt M}_{\,r}$ is the common VRF message computed in round $r$ and $\epsilon$ a predefined threshold. See Section~\ref{sec:beacon} for details of the computation of ${\tt M}_{\,r}$. Given the VRF proof and the corresponding public key, anyone can verify the membership claimed by $u$ by Algorithm~\ref{alg:endorse-valid} as shown below.

\begin{algorithm}[H]
\caption{Procedure for $u$ to determine his committee membership. }
\label{alg:committee-gen}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Compute ${\tt M}_{\,r}$
    \State Compute $\pi_{u,r} = \Pi_{vrf}({\tt SK}_u,{\tt M}_{\,r})$ and $\lambda=H\left(\pi_{u,r}\right)$
    \vspace{1ex}
    \If{$\lambda\leq\epsilon$}
        \State Return $\left({\tt TRUE},\pi_{u,r}\right)$
    \Else 
        \State Return {\tt FALSE}
    \EndIf
\end{algorithmic}
\end{spacing}
\end{algorithm}

\begin{algorithm}[H]
\caption{Procedure for anyone to validate $u$'s claimed committee membership.}
\label{alg:committee-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Compute ${\tt M}_{\,r}$
    \vspace{1ex}
    \If{$V_{vrf}({\tt PK}_u,\pi_{u,r})={\tt FALSE}$}
        \State Return {\tt FALSE}
    \EndIf
    \vspace{1ex}
    \State $\lambda\leftarrow H(\pi_{u,r})$
    \vspace{1ex}
    \If{$\lambda\leq\epsilon$}
        \State Return {\tt TRUE}
    \Else 
        \State Return {\tt FALSE}
    \EndIf
\end{algorithmic}
\end{spacing}
\end{algorithm}

@@

\subsection{Canonical Chain Rule}
In this subsection, we provide the rules for selecting the canonical chain (or the \textit{trunk}) based on the committee mechanism. Let $\omega$ be a branch, i.e., a chain of blocks. Given a block~$B$ on the branch, i.e.,~$B\in\omega$, we define the weight of the chain starting from $B$ till the end of $\omega$,~$W(\omega,B)$, as the size of the set that contains all the leaders and committee members who have their signatures included in at least one block on the chain. Note that a node is only counted once.

Given two branches $\omega_1$ and $\omega_2$, let $B_0$ be the last block shared by $\omega_1$ and $\omega_2$, i.e., $B_0\in\omega_1\cap\,\omega_2$ and $\forall\, B'\in\omega_1\cap\,\omega_2,\, B'\preceq B_0$. Let $N(\omega,B)$ be the operator that finds the next block of $B$ on branch~$\omega$. We choose the canonical chain~$\omega^*$ from two branches~$\omega_1$ and $\omega_2$ by Algorithm~\ref{alg:canonical-chain} as shown below:

\begin{algorithm}[H]
\caption{Rules for choosing canonical chain~$\omega^*$ from branches~$\omega_1$ and $\omega_2$.}
\label{alg:canonical-chain}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State $B_1\leftarrow N(\omega_1,B_0)$
    \State $B_2\leftarrow N(\omega_2,B_0)$
    \vspace{1ex}
    \While{$W(\omega_1,B_1)=W(\omega_2,B_2)$ \textbf{and} $N(\omega_1,B_1)\neq{\tt nil}$ \textbf{and} $N(\omega_2,B_2)\neq{\tt nil}$}
        \State $B_1\leftarrow N(\omega_1,B_1)$
        \State $B_2\leftarrow N(\omega_2,B_2)$
    \EndWhile
    \vspace{1ex}
    \If{$W(\omega_1,B_1)>W(\omega_2,B_2)$}
        \State $\omega^*\leftarrow\omega_1$
    \ElsIf{$W(\omega_1,B_1)<W(\omega_2,B_2)$}
        \State $\omega^*\leftarrow\omega_2$
    \Else
        \If{$B_1$ is published later than $B_2$}
            \State $\omega^*\leftarrow\omega_1$
        \Else
            \State $\omega^*\leftarrow\omega_2$
        \EndIf
    \EndIf
\end{algorithmic}
\end{spacing}
\end{algorithm}

>>>>

\section{Overview}
The Proof-of-Authority consensus algorithm~\cite{VWP18}, or PoA in short, is efficient of using network bandwidth. It divides time into rounds with a fixed length and assumes that the majority of its (authorized) nodes perform consensus in the same round. In each round, nodes select a leader (the node responsible for generating a new block) based on the round number, block height and their local views of the active nodes. Therefore, the procedure can be considered instant, which allows more time for transmitting transaction (TX) data in each consensus round.

However, PoA cannot prevent a malicious leader from causing temporary inconsistency by producing multiple blocks. To improve the security of PoA, we propose to introduce a committee (a group of selected nodes) to endorse the new block generated in each consensus round. The verifiable random function~(VRF)~\cite{PapEtAl99} is used for committee selection in each round. With the committee mechanism, a malicious leader would have to collude with committee members to cause inconsistency. However, the property of VRF guarantees that the committee is selected randomly. Therefore, it makes it much more difficult for adversaries to launch such attacks.

It is assumed that the network is synchronous and the messages are transmitted through gossip communication, i.e., if an honest node sends a message or an honest node receives a message, all other honest nodes will receive same message within at most a delay of $\tau$, which is determined by the network configuration and is known in advance.

%Note that besides the network synchrony, we also assume that messages be transmitted through gossip communication. Hence, if an honest node receives a message, all other honest nodes will receive the same message with a bounded delay. 
\section{Specifications}
\subsection{Notations}
\renewcommand{\arraystretch}{2}
\begin{longtable}{p{3cm} p{10cm}}
    Symbol  & Description \\
    \hline\hline
    $N$ & Total number of nodes \\
    \hline
    $u=1,2,\dots,N$ & node index \\
    \hline
    $H(\cdot)$ & Cryptographic hash function \\
    \hline
    ${\tt SIG}_u(\cdot)$ & Signature of $u$ \\
    \hline
    $\left({\tt PK}_u,{\tt SK}_u\right)$ & Public and private keys generated by $u$ to sign blocks \\
    \hline
    $\rho\left(\cdot\right)$ & Merkle root of the input set\\
    \hline
    $r$ & Consensus round number \\
    \hline
    $l_r=1,2,...,N$ & Leader in round $r$ \\
    \hline
    $s_r$ & Block summary produced by $l_r$ \\
    \hline
    $\tau_r$ & $s_r\,\|\,{\tt Sig}_{\,l_r}(s_r)$ \\
    \hline
    $\epsilon$ & Predefined threshold to determine committee membership \\
    \hline
    $d$ & Number of endorsements required to produce a valid block \\
    \hline
    $\Sigma_r$ & Transaction set prepared by $l_r$ \\
    \hline
    $B_{u,r}^*$ & Last block of the canonical chain (trunk) recognized by $u$ in round $r$\\ 
    \hline
    $H_{vrf},\Pi_{vrf},V_{vrf}$ & Functions that compute hash, generate proof and verify proof defined in the VRF scheme, respectively \\
    \hline
    $\left({\tt PK}_u^{vrf},{\tt SK}_u^{vrf}\right)$ & Public and private key pair generated by $u$ for VRF  \\
    \hline
    ${\tt M}_{\,r}$ & Common VRF message generated for committee selection \\
    \hline
    % $\omega$, $\omega^*$ & Branch and trunk \\
    % \hline
    $m$, $L$ & Epoch number and the number of consensus rounds in one epoch \\
    \hline
    $b_m$ & Random beacon computed using randomness from the last block of the $m$'th epoch \\
    \hline
\end{longtable}

\subsection{Committee Membership}
\label{sec:committee}
The verifiable random function can be considered a public-key version of keyed cryptographic hash. The hash of a given message can only be computed by the owner of the private key and can be verified by anyone given the public key~{\tt SK} and message~{\tt M}. The scheme defines the following functions:
\begin{itemize}
    \item $\pi\leftarrow\Pi_{vrf}({\tt SK},{\tt M})$ - function that generates VRF proof;
    \item $\{{\tt TRUE}, {\tt FALSE}\}\leftarrow V_{vrf}({\tt SK},{\tt M},\pi)$ - function that verify VRF proof;
    \item $h\leftarrow H_{vrf}({\tt SK},{\tt M})=H(\pi)$ - function that computes the hash.
\end{itemize}

Node~$u$ determines his committee membership by Algorithm~\ref{alg:committee-gen}. Here ${\tt M}_{\,r}$ can be locally computed by each node in a deterministic way and $\epsilon$ a predefined threshold. See Section~\ref{sec:beacon} for details of how to compute ${\tt M}_{\,r}$. Given the VRF proof~$\pi_{u,r}$ and the corresponding public key~${\tt PK}_u^{vrf}$, anyone can verify the membership claimed by $u$ by Algorithm~\ref{alg:committee-valid} below.

\begin{algorithm}[H]
\caption{Procedure for $u$ to determine his committee membership. }
\label{alg:committee-gen}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Compute ${\tt M}_{\,r}$
    \State Compute $\pi_{u,r} = \Pi_{vrf}({\tt SK}_u^{vrf},{\tt M}_{\,r})$ and $\lambda=H\left(\pi_{u,r}\right)$
    \vspace{1ex}
    \If{$\lambda\leq\epsilon$}
        \State Return $\left({\tt TRUE},\pi_{u,r}\right)$
    \Else 
        \State Return {\tt FALSE}
    \EndIf
\end{algorithmic}
\end{spacing}
\end{algorithm}

\begin{algorithm}[H]
\caption{Procedure for anyone to validate $u$'s claimed committee membership.}
\label{alg:committee-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Compute ${\tt M}_{\,r}$
    \vspace{1ex}
    \If{$V_{vrf}({\tt PK}_u^{vrf},\pi_{u,r})={\tt FALSE}$}
        \State Return {\tt FALSE}
    \EndIf
    \vspace{1ex}
    \State $\lambda\leftarrow H(\pi_{u,r})$
    \vspace{1ex}
    \If{$\lambda\leq\epsilon$}
        \State Return {\tt TRUE}
    \Else 
        \State Return {\tt FALSE}
    \EndIf
\end{algorithmic}
\end{spacing}
\end{algorithm}

@@

% \subsection{Canonical Chain Rule}
% In this subsection, we provide the rules for selecting the canonical chain (or the \textit{trunk}) based on the committee mechanism. Let $\omega$ be a branch, i.e., a chain of blocks. Given a block~$B$ on the branch, i.e.,~$B\in\omega$, we define the weight of the chain starting from $B$ till the end of $\omega$,~$W(\omega,B)$, as the size of the set that contains all the leaders and committee members who have their signatures included in at least one block on the chain. Note that a node is only counted once.

% Given two branches $\omega_1$ and $\omega_2$, let $B_0$ be the last block shared by $\omega_1$ and $\omega_2$, i.e., $B_0\in\omega_1\cap\,\omega_2$ and $\forall\, B'\in\omega_1\cap\,\omega_2,\, B'\preceq B_0$. Let $N(\omega,B)$ be the operator that finds the next block of $B$ on branch~$\omega$. We choose the canonical chain~$\omega^*$ from two branches~$\omega_1$ and $\omega_2$ by Algorithm~\ref{alg:canonical-chain} as shown below:

% \begin{algorithm}[H]
% \caption{Rules for choosing canonical chain~$\omega^*$ from branches~$\omega_1$ and $\omega_2$.}
% \label{alg:canonical-chain}
% \begin{spacing}{1.2}
% \begin{algorithmic}[1]
%     \vspace{1ex}
%     \State $B_1\leftarrow N(\omega_1,B_0)$
%     \State $B_2\leftarrow N(\omega_2,B_0)$
%     \vspace{1ex}
%     \While{$W(\omega_1,B_1)=W(\omega_2,B_2)$ \textbf{and} $N(\omega_1,B_1)\neq{\tt nil}$ \textbf{and} $N(\omega_2,B_2)\neq{\tt nil}$}
%         \State $B_1\leftarrow N(\omega_1,B_1)$
%         \State $B_2\leftarrow N(\omega_2,B_2)$
%     \EndWhile
%     \vspace{1ex}
%     \If{$W(\omega_1,B_1)>W(\omega_2,B_2)$}
%         \State $\omega^*\leftarrow\omega_1$
%     \ElsIf{$W(\omega_1,B_1)<W(\omega_2,B_2)$}
%         \State $\omega^*\leftarrow\omega_2$
%     \Else
%         \If{$B_1$ is published later than $B_2$}
%             \State $\omega^*\leftarrow\omega_1$
%         \Else
%             \State $\omega^*\leftarrow\omega_2$
%         \EndIf
%     \EndIf
% \end{algorithmic}
% \end{spacing}
% \end{algorithm}
